EvoSuite at the SBST 2017 Tool Competition

### 2017-02-21 papers/sbst17/paper_sbst17.tex
dd.

% Look at benchmarks with more flaky tests
Flaky tests continue to be a challenge for test generation. Benchmarks
FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
tests in one run (12 and 14, respectively). In both cases, the
minimisation phase timed out and hence \EVOSUITE reverted the
resulting test suite to the previous, unminimised one, which as
mentioned before, is more likely to break. Partial minimisation might
be worth investigating to alleviate this issue.

>>>>

% Look at benchmarks with more flaky tests
Flaky tests continue to be a challenge for test generation. Benchmarks
FREEHEP-7 and JXPATH-10 were the ones with the highest number of flaky
tests in one run (12 and 14, respectively). In both cases, the
minimisation phase timed out and hence \EVOSUITE reverted the
resulting test suite to the previous, unminimised one, which as
mentioned before, is more likely to break. Techniques such as
\textit{partial minimisation} to only select a few test cases to be
minimised, rather than all test cases; or
\textit{delta-debugging}~\cite{zellerdd}, which could isolate the
relevant statements of each test case, might be worth investigating
to alleviate this issue.
